SPARQL on the open, decentralised Web

### 2016-06-21 dissertation/related.tex
Add discussion of Semantic caching #10

>>>>

As such, this mirrors an extensive development known as ``Semantic
Caching'' in the database community. Ahmad et al. \cite{4777801}
surveyed the state of the art in that area. They divided caching
approaches into \emph{page}, \emph{tuple} and \emph{semantic} caches,
and noted that in the two former cases, if only partial results were
available in the cache, the entire result would have to be fetched
from the remote database. Indeed, a page or tuple cache may be used to
cache the results of a whole SPARQL query in HTTP context, but SPARQL
queries are also trivial to partition by e.g. triple patterns or Basic
Graph Patterns, which provides further opportunities for caching where
only partial results are available.\todo{Have I understood this correctly?}
